Predicting the Capture Rate of Pokemon

### 2023-04-06 Predicting_Pokemon_Capture_Rate.Rmd
final commit
edits

---
title: "Predicting the Capture Rate of Pokemon"
subtitle: "PSTAT 131 Final Project"
author: "Shivani Kharva"
date: "2022-12-11"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    df_print: paged
    theme: journal
---

@@

However, a question I'd like to pose is "How hard is to capture a Pokemon in the first place depending on their existing statistics?" It seems quite reasonable to hypothesize that a Pokemon's capture rate would vary depending on variables like their type, base statistics, generation, etc. So, I would like to test if it is possible to develop a model that can predict the capture rate of a Pokemon based on those qualities.

@@

One last thing we need to do before our data is tidy the `abilities` variable because we currently have a column made up of lists of each Pokemon's abilities. However, it is not very useful to analyze 801 unique lists of abilities. It might be better to prioritize the abilities that are the most common among the Pokemon. Let's look at the top 5 most common abilities and their capture rates.

@@

### Type 1 Plot

>>>>

---
title: "Predicting the Capture Rate of Pokemon"
author: "Shivani Kharva"
date: "2022-12-11"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    df_print: paged
    theme: journal
  pdf_document:
    toc: yes
subtitle: PSTAT 131 Final Project
---

@@

However, a question I'd like to pose is "How hard is it to capture a Pokemon in the first place depending on their existing statistics?" It seems quite reasonable to hypothesize that a Pokemon's capture rate would vary depending on variables like their type, base statistics, generation, etc. So, I would like to test if it is possible to develop a model that can predict the capture rate of a Pokemon based on those qualities.

@@

One last thing we need to do before our exploratory data analysis is tidy the `abilities` variable because we currently have a column made up of lists of each Pokemon's abilities. However, it is not very useful to analyze 801 unique lists of abilities. It might be better to prioritize the abilities that are the most common among the Pokemon. Let's look at the top 5 most common abilities and their capture rates.

@@

### Type 1
